Title

### 2013-03-18 main.tex
introduction to hardware is now its own file

  \begin{figure}
    \centering
    \includegraphics{inc/hardware/column.jpg}
    \caption[Picture of the prototype UEM column at UIC]{
      Picture of the majority of the prototype UEM column at UIC.
      The main vacuum chamber is laid sideways, with the high voltage (gun) at the left and the imaging system on the right.
      The magnetic levitated turbo pump hangs below the column, a scroll pump used for backing is not pictured.
      The laser system is in the background.
      All of the above is mounted on a custom shaped active vibration-canceling optical table.
      The electronic control systems are not pictured.
    }
    \label{fig:column-pic}
  \end{figure}

>>>>

  \subimport{inc/hardware/}{introduction}
